Retrofitting Effect Handlers onto OCaml

### 2020-11-20 retro-concurrency.tex
Conclusions

%\vspace{-3mm}
\section{Conclusions}
\label{sec:conc}

Our design for effect handlers in OCaml walks the tightrope of maintaining
compatibility (for profiling, debuggers and negligible overheads for existing
programs), while unlocking the full power of non-local control flow constructs.
Our evaluation shows that we have achieved our goal: we retain compatibility
with a surprisingly low performance overhead for sequential code that preserves
the spirit of ``fast exceptions'' that has always characterised OCaml
programming. We believe that the introduction of lightweight fibers to support
effect handlers into OCaml -- along with a parallel
runtime~\cite{Sivaramakrishnan20} -- will open OCaml to highly task-parallel
applications with minimal hit to sequential performance.

>>>>

\vspace{-3mm}
\section{Conclusions}
\label{sec:conc}

Our design for effect handlers in OCaml walks the tightrope of maintaining
compatibility (for profiling, debuggers and negligible overheads for existing
programs), while unlocking the full power of non-local control flow constructs.
Our evaluation shows that we have achieved our goal: we retain compatibility
with a surprisingly low performance overhead for sequential code that preserves
the spirit of ``fast exceptions'' that has always characterised OCaml
programming. We believe that the introduction of effect handlers into OCaml
implemented using lightweight fibers, along with a parallel
runtime~\cite{Sivaramakrishnan20}, will open OCaml to highly scalable
concurrent and task-parallel applications with minimal hit to sequential
performance.
